О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
which -> that (due to importance)
Edit a lemma cosmetically

Now we will estimate the length of a line segment, which shares an arbitrary number of points
with an integral point set.

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta| = l$ and $M \in \mathfrak{M}(2,n)$.
	Let $\#(\Delta \cap M) = t$.
	Then $l\geq \frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5}{6}t^{1/2}$.
\end{lemma}

>>>>

Now we will estimate the length of a line segment that shares an arbitrary number of points
with an integral point set.

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta| = b$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = t$.
	Then
	\begin{equation}
		\label{eq:estimate_for_segment_length}
		b\geq \frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5}{6}t^{1/2}
		.
	\end{equation}
\end{lemma}
